1-Define Data

### 2024-11-01 1definedata.Rmd
definedatapush2

I tried removing the discipline = "sociology" part in the fcolnet and all following functions that select data BUT SINCE 'discipline' is also relevant in the rest of the functions' code, it does not end up doing what I hoped (having a dataset with scholars of no specific discipline because then I could hopefully check how the department is named in the data and then find out how to add that to the data set initially).

@@

#after taking out discipline= "sociology" in this first part    
f_pubnets <- function(df_scholars = df, list_publications = publications, affiliation = "RU",
    wave = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {

@@

@@

```{r}
# dependent
    # not using net_soc_array for now since I am unsure about its use due to question above
# net <- sienaDependent(net_soc_array)

@@

```{r, include=FALSE}
# Add h-index and i10-index columns to df_ego
df_ego <- df_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

@@

view(data('discipline'))
```

>>>>

I tried removing the discipline = "sociology" part in the f_pubnets, fcolnet and all following functions that select data BUT SINCE 'discipline' is also relevant in the rest of the functions' code, it does not end up doing what I hoped (having a dataset with scholars of no specific discipline because then I could hopefully check how the department is named in the data and then find out how to add that to the data set initially).

@@

#after taking out discip = "sociology" in this first part    
f_pubnets <- function(df_scholars = df, list_publications = publications, affiliation = "RU",
    wave = list(wave1 = c(2018, 2019, 2020), wave2 = c(2021, 2022, 2023))) {

@@

## My data

@@

```{r}
# dependent
# net <- sienaDependent(net_soc_array)

@@

```{r}
# Add h-index and i10-index columns to df_ego
df_ego <- df_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

@@
